### 2020-07-20 article.tex
Additional comment about CISS

additional command line argument \pk{-eps\_type ciss}. Blocking is also
available and tested in SLEPc test suite for \pk{EPSSUBSPACE} and
\pk{NEPCISS} since version 3.14.0.

>>>>

additional command line argument \pk{-eps\_type ciss}.
However, this eigensolver is mostly suited for finding interior eigenpairs.
For fairness, its performance is not reported, but the options from the script
can be readily used for problems where \pk{EPSCISS} is an appropriate solver.
Blocking is also available and tested in SLEPc test suite for \pk{EPSSUBSPACE}
and \pk{NEPCISS} since version 3.14.0.
